Checklist

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] personal checklist

\newcommand\DevDef[2]{
  \begin{minipage}{\linewidth}
    \begin{itemize}
    \item\DevHeader{#1}
      #2
    \end{itemize}
    \vspace{0.8cm}
  \end{minipage}
}
\newcommand\Person[1]{
\clearpage
\section{#1}
\fancyhead[R]{#1}
\setcounter{page}{1}
For shutting off, go through the checklist in the following order
\begin{itemize}
\item\OffBox Turn off equipments
\item\OffBox Turn off power supplies
\item\OffBox Turn off computers
\end{itemize}
Wait before everyone else finish their corresponding steps before starting the next one.\\
For powering up, go through the checklist in the following order
\begin{itemize}
\item\OnBox Turn on computers
\item\OnBox Turn on power supplies
\item\OnBox Turn on equipments
\item\OnBox Check computer connection to devices
\end{itemize}
Also wait before everyone else finish their corresponding steps before starting the next one.
}

@@

\Person{Yichao}
\section{Equipments}
\section{Power supplies}
\section{Computers}
\Person{Jon}
\section{Equipments}
\section{Power supplies}
\section{Computers}
\Person{Lee}
\section{Equipments}
\section{Power supplies}
\section{Computers}
\Person{Jessie}
\section{Equipments}
\section{Power supplies}
\section{Computers}
\Person{Frederic}
\section{Equipments}
\section{Power supplies}
\section{Computers}

\DevDef{Andor Camera for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
}
\DevDef{Andor Camera for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
}
\DevDef{Tweezer 1 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Thorlabs cameras
  \item\OnBox Na Raman amplifier
  \end{itemize}
}
\DevDef{Tweezer 2 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \end{itemize}
}
\DevDef{Tweezer 3 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Software radio
  \end{itemize}
}
\DevDef{Tweezer 4 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \item\OnBox Thorlabs camera
  \end{itemize}
}
\DevDef{PLL for 1.0 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{PLL for 1.0 Cs Raman}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{PLL for 1.5 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings ???
  \end{itemize}
}
\DevDef{1.5 Feshbach coils}{
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
}
\DevDef{1.5 IGBT}{
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
}
\DevDef{Computer control box for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
}
\DevDef{Computer control box for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the left side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
  \item\OnBox Turn on the power switch of the box.
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Switch off/on the front switch
}
\DevDef{Benchtop power supply}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{1st version Till's current controller for Cs MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record current value:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Homebuilt $\pm15,5$V power supply}{
  \textbf{2nd level above Cs tweezer/MOT lasers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Cs 1.0 MOT lock box}{
  \textbf{1st level above Cs MOT lasers}
  \begin{itemize}
  \item\OffBox Make sure the laser is unlocked.
  \end{itemize}
}
\DevDef{Novatech function generator}{
  \textbf{1st level above Cs MOT lasers}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Save settings
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Restore settings
  \end{itemize}
}
\DevDef{New Focus Cs Raman lasers drivers (2x)}{
  \textbf{1st level above Cs Raman lasers}\\
  Record Temperature, Current, Piezo voltage\\
  Temperature is accessible in the menu under system status\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox (Turn on)
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{1st level next to Cs Raman driver}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above Cs Raman lasers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{SRS shutter driver for Cs}{
  \textbf{1st level above Cs Raman lasers}\\
  Switch off/on with the switch on the back.
}
\DevDef{New Focus lock box for Cs Raman}{
  \textbf{1st level above Cs Raman lasers}\\
  Unplug power.
}
\DevDef{Benchtop power supply for Cs Raman locking}{
  \textbf{2nd level above Cs Raman lockbox}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record current and T1 settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \item\OnBox Set current/temperature.
  \item\OnBox Enable T1 survo
  \item\OnBox Turn on current
  \end{itemize}
}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Na D2}{
  \textbf{1st level above Na seed}\\
  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
  Record high voltage power supply output

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Turn down the voltage of the high voltage power supply to 0
  \item\OffBox Unplug high voltage power on lockbox (zip tie)
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \item\OffBox Turn off high voltage power supply
  \item\OffBox Unplug high voltage power supply from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug high voltage power supply into the wall
  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
  \item\OnBox Plug in 15V to lockbox
  \item\OnBox Plug in high voltage to lockbox
  \item\OnBox Turn up the voltage of the high voltage power supply
  \item\OnBox Check HV output
  \end{itemize}
}
\DevDef{Oscilloscope for Na D2 lock}{
  \textbf{1st level above Na Raman amplifier}
  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}
\DevDef{MPB Raman amplifier}{
  \textbf{1st level above Na MOT beam path}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Power off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Power on
  \end{itemize}
}
\DevDef{Variac for Na cell}{
  \textbf{Above Na D2 beam path}\\
  Record temperature and voltage settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn voltage to 0
  \item\OffBox Switch off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Switch on
  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
  \end{itemize}
}
\DevDef{SRS shutter driver for Na}{
  \textbf{1st level above Na D2 beam path, below Variac}\\
  Switch off/on with the switch on the back.
}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Na Variac}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Na D1}{
  \textbf{1st level above Na D2 beam path}\\
  \textbf{Turn on-off together with the fixed high voltage power supply above}\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check current setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Na D1 seed controllers}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above Cs tweezer controllers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for Cs tweezer}{
  \textbf{1st level above Cs tweezer}\\
  Switch off/on the front switch
}
\DevDef{2nd version Till's current controller for Cs Tweezer}{
  \textbf{1st level above Cs tweezer}\\
  Record current value:\\

>>>>

\newcommand\DevDef[2]{
  \begin{minipage}{\linewidth}
    \begin{itemize}
    \item\DevHeader{#1}
      #2
    \end{itemize}
    \vspace{0.8cm}
  \end{minipage}
}
\newcommand\Person[1]{
\clearpage
\section*{#1}
\fancyhead[R]{#1}
\setcounter{page}{1}
\setcounter{subsection}{0}
For shutting off, go through the checklist in the following order
\begin{itemize}
\item\OffBox Turn off equipments
\item\OffBox Turn off power supplies
\item\OffBox Turn off computers
\end{itemize}
Wait before everyone else finish their corresponding steps before starting the next one.\\
For powering up, go through the checklist in the following order
\begin{itemize}
\item\OnBox Turn on computers
\item\OnBox Turn on power supplies
\item\OnBox Turn on equipments
\item\OnBox Check computer connection to devices
\end{itemize}
Also wait before everyone else finish their corresponding steps before starting the next one.
}
\renewcommand{\thesubsection}{\arabic{subsection}}

@@

\Person{Yichao}
\subsection{Equipments}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record current and T1 settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \item\OnBox Set current/temperature.
  \item\OnBox Enable T1 survo
  \item\OnBox Turn on current
  \end{itemize}
}
\DevDef{Oscilloscope for Na D2 lock}{
  \textbf{1st level above Na Raman amplifier}
  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}
\DevDef{MPB Raman amplifier}{
  \textbf{1st level above Na MOT beam path}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Power off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Power on
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Na D2}{
  \textbf{1st level above Na seed}\\
  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
  Record high voltage power supply output

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Turn down the voltage of the high voltage power supply to 0
  \item\OffBox Unplug high voltage power on lockbox (zip tie)
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \item\OffBox Turn off high voltage power supply
  \item\OffBox Unplug high voltage power supply from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug high voltage power supply into the wall
  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
  \item\OnBox Plug in 15V to lockbox
  \item\OnBox Plug in high voltage to lockbox
  \item\OnBox Turn up the voltage of the high voltage power supply
  \item\OnBox Check HV output
  \end{itemize}
}
\DevDef{SRS shutter driver for Na}{
  \textbf{1st level above Na D2 beam path, below Variac}\\
  Switch off/on with the switch on the back.
}
\DevDef{Variac for Na cell}{
  \textbf{Above Na D2 beam path}\\
  Record temperature and voltage settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn voltage to 0
  \item\OffBox Switch off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Switch on
  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Na D1}{
  \textbf{1st level above Na D2 beam path}\\
  \textbf{Turn on-off together with the fixed high voltage power supply above}\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check current setting
  \item\OnBox Turn on
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Na Variac}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above Cs tweezer controllers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Na D1 seed controllers}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{1st level above Cs tweezer}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
}
\Person{Jon}
\subsection{Equipments}
\DevDef{Agilent function generator for Na 1.0 switching}{
  \textbf{1st level above TiSapph facing computers}\\
  Record parameters:\\

  \begin{tabular}{|c|c|}
    \hline
    Ch1 Hi&\hphantom{\hspace{3.5cm}}\\\hline
    Ch1 Lo&\\\hline
    Ch2 Hi&\\\hline
    Ch2 Lo&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Turn on
  \item\OnBox Set frequency, duty cycle, high/low voltages
  \item\OnBox Set switching phase back
  \end{itemize}
}
\DevDef{2nd version Till's current controller for Cs 1.5 (x2)}{
  \textbf{1st level above 1.5 Cs MOT}\\
  Record current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Thorlabs current controller}{
  \textbf{1st level below Cs 1.5 MOT drivers}\\
  Unused\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for Cs 1.5 MOT (x2)}{
  \textbf{1st level above Cs 1.5 MOT}\\
  Switch off/on the front switch
}
\DevDef{Oscilloscope for Cs 1.5 MOT lock}{
  \textbf{1st level above Cs 1.5 MOT}
  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Cs 1.5 MOT}{
  \textbf{1st level above Cs 1.5 MOT}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in 15V to lockbox
  \end{itemize}
}
\DevDef{Function generator for Cs MOT 1.5 lockbox}{
  \textbf{1st level under Cs MOT 1.5 lockbox}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Record settings
  \item\OffBox Turn off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Turn on
  \item\OnBox Restore settings
  \end{itemize}
}
\DevDef{HV amplifiers for 1.0 piezo mirrors}{
  \textbf{Above the space beween Na 1.5 beam path and NaCs 1.5 chamber}\\
  \textbf{Turn on-off together with the function generator below
    and the high voltage power supply on the left}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off the function generator
  \item\OffBox Unplug function generator output (zip tie and label)
  \item\OffBox Unplug HV power supply from the wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin HV power supply to the wall
  \item\OnBox Plugin function generator output
  \item\OnBox Turn on the function generator
  \end{itemize}
}
\DevDef{Pump}{
  \textbf{1st level above NaCs 1.0 chamber}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug from walls
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Turn on (should be enough)
  \end{itemize}
}
\DevDef{Andor Camera for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Cs 1.5 MOT controllers}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above Cs 1.5 MOT controllers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply (x2)}{
  \textbf{1st level above Na 1.5 bean path}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $\pm15,5$V power supply}{
  \textbf{2nd level above Na 1.5 beam path}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply (x2)}{
  \textbf{2nd level above piezo mirror electronics}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above NaCs 1.0 chamber}\\
  Record voltage/current values:\\
